\documentclass{bilal}
\name{Bilal Abdul Halim}
\address{1001 N Byrne Rd \\ Toledo, Ohio 43607}
\address{(567)~$\cdot$~698~$\cdot$~0941 \\ Bilal.AbdulHalim@rockets.utoledo.edu}
\begin{document}
\begin{rSection}{Education}
{\bf University of Toledo, Toledo, Ohio} \hfill {\em August 2020 -- May 2022} \\
Master's of Science in Mechanical Engineering \\
Concentration in Fluid Mechanics \smallskip \\
Overall GPA: 4.0

{\bf University of Toledo, Toledo, Ohio} \hfill {\em August 2015 -- May 2020} \\
Bachelor's of Science in Mechanical Engineering \\
Concentration in Applied Mathematics \smallskip \\
Overall GPA: 3.9
\end{rSection}
\begin{rSection}{Experience}
\begin{rSubsection}{University of Toledo}{May 2020 -- Present}{Graduate Researcher}{Toledo, Ohio}
\item Simulated and studied crack formation in ice using Abaqus.
\item Implemented the Abaqus Python modules to script and post process data.
\item Optimized Abaqus jobs to run on the Ohio Super Computer using Unix Shell commands.
\item Prepared and presented reports and presentation using Markdown and \LaTeX.
\end{rSubsection}
\begin{rSubsection}{Learning Enhancement Center}{October 2016 -- May 2020}{Engineering \& Mathematics Tutor}{Toledo, Ohio}
\item Tutored students individually and in groups all fundamental Mathematics and Engineering courses.
\item Guided students through complex mathematical and engineering problems.
\item Encouraged independent learning through different techniques.
\item Managed and trained new tutors on different skills and techniques.
\end{rSubsection}
\begin{rSubsection}{Plastic Technologies Inc}{January 2019 -- August 2019}{Finite Element Analysis Engineer}{Holland, Ohio}
\item Translated various physical problems to accurate FEA models.
\item Conducted stress and thermal analysis on different plastic packages.
\item Improved company's R\&D department through Abaqus Scripting (Python).
\item Worked closely with the design team providing suggestions based on FEA results.
\item Guided customers to an optimum package design through iterative FEA.
\item Wrote and organized proposals and reports for customers.
\end{rSubsection}
\begin{rSubsection}{PICSSL}{June 2017 -- January 2019}{Material Science Researcher}{Toledo, Ohio}
\item Lead a project on pressure-sensitive foams.
\item Conducted a plethora of polymer characterizations XRD, DSC, SEM, FTIR, UV VIS.
\item Designed and built a setup for in-situ pressure vs. transparency measurements, with a published patent.
\item Utilized Python and Excel to interpret data, generate high-quality charts and propose hypotheses.
\item Presented proposals and reports for specialized faculty members.
\end{rSubsection}
\end{rSection}
\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
FEA \& CAD & Abaqus, SolidWorks, NX, Autocad \\
Software \& OS & Microsoft Office Suite, Linux, Vim \\
Computer Languages & Python, MATLAB, C, AWK, Bash, \LaTeX \\
\end{tabular}
\end{rSection}
\end{document}
